Observed vs. Simulated Year Comparison

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Store the ratio summaries for all estimated quantities

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb_per_f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Egg to Parr Survival: Estimates")
ratio_plots(x, "Egg to Parr Survival: Ratios")
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^pi[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Fall Migrants: Estimates")
ratio_plots(x, "Proportion Fall Migrants: Ratios")
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Overwinter Survival: Estimates")
ratio_plots(x, "Overwinter Survival: Ratios")
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Migration to LGR Survival: Estimates")
ratio_plots(x, "Migration to LGR Survival: Ratios")
```

@@

```{r}
x = append(
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "LGR to Ocean Survival: Estimates")
ratio_plots(x, "LGR to Ocean Survival: Ratios")
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "First Year Ocean Survival: Estimates")
ratio_plots(x, "First Year Ocean Survival: Ratios")
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-3 Maturity: Estimates")
ratio_plots(x, "Age-3 Maturity: Ratios")
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-4 Maturity: Estimates")
ratio_plots(x, "Age-4 Maturity: Ratios")
```

@@

```{r}
x = append(
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "BON to LGR Survival: Estimates")
ratio_plots(x, "BON to LGR Survival: Ratios")
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^phi_Sb_Sa[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Pre-Spawn Survival: Estimates")
ratio_plots(x, "Pre-Spawn Survival: Ratios")
```

>>>>

```{r}
est_ratios = NULL
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb_per_f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Egg to Parr Survival: Estimates")
ratio_plots(x, "Egg to Parr Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Egg to Parr Survival"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^pi[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Proportion Fall Migrants: Estimates")
ratio_plots(x, "Proportion Fall Migrants: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Proportion Fall Migrants"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Pa_Mb[year,LH_type,pop]", obs_y, sim_y, pop = j, LH_type = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Overwinter Survival: Estimates")
ratio_plots(x, "Overwinter Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Overwinter Survival"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 1)),
  lapply(1:4, function(j) get_ratio("^phi_Mb_Ma[year,LH_type,origin,pop]", obs_y, sim_y, pop = j, LH_type = 2, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Migration to LGR Survival: Estimates")
ratio_plots(x, "Migration to LGR Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Migration to LGR Survival"))
```

@@

```{r}
x = append(
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Ma_O0[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "LGR to Ocean Survival: Estimates")
ratio_plots(x, "LGR to Ocean Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "LGR to Ocean Survival"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("phi_O0_O1[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "First Year Ocean Survival: Estimates")
ratio_plots(x, "First Year Ocean Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "First Year Ocean Survival"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-3 Maturity: Estimates")
ratio_plots(x, "Age-3 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-3 Maturity"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-4 Maturity: Estimates")
ratio_plots(x, "Age-4 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-4 Maturity"))
```

@@

```{r}
x = append(
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("^phi_Rb_Ra[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "BON to LGR Survival: Estimates")
ratio_plots(x, "BON to LGR Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "BON to LGR Survival"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^phi_Sb_Sa[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Pre-Spawn Survival: Estimates")
ratio_plots(x, "Pre-Spawn Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "Pre-Spawn Survival"))
```
